---
title: "Data Science Programs offered in the US"
author: "elobo"
date: "23/10/2016"
output: ioslides_presentation
---

## Synopsis

This presentation wants to ilustrate a quick view on a shiny app designed to show list of programs related to Data Science field offered by different schools along the Unated States.

Dataset is available at Kaggle [link](https://www.kaggle.com/sriharirao/datascience-universities-across-us)


## Overview of the app

In order to use the app, the user must select which US State he is interested to check, and a summary of program registered by schools on that state will summarize into a bar plot. There is the possibily of choosing the type of program: Master or Certification degree.

In order to inspect results, the info is distributed into three main panel. 

* One panel for ginving general documentation
* Other panel to check the programs by shcools and 
* A last panel to check program duration.

Finally, a calculation showing the amount of programs given for that state is shown and the bottom of program panel.

Shiny app is available at this shinyapp.io [link](http://edlobo.shinyapps.io/FInalC9/)

## Shiny app

```{r code1, echo = FALSE, message=FALSE, eval=TRUE}

library(dplyr)
library(ggplot2)
data <- read.csv("/Users/elobo/HomeRstudio/Curso9/Shiny/DSuniversity/data/timesMergedData.csv")
# check cols with NA
        calc_NA <- function(x){sum(is.na(x))/length(x)*100}
        check_NA <- as.data.frame(apply(data,2,calc_NA))
# check with numbers
# table(check_NA[,1] > 20.0)
# take off columns with NAs
        valid <- check_NA[,1] > 20.0
        validnames <- rownames(check_NA)[!valid]

finaldf <- data[,validnames]
finaldf <- unique(finaldf)
minidf <- finaldf %>% filter(STATE=="Washington", TYPE=="M")
```

Shiny output when choosing a particular state

```{r code2, echo = FALSE, eval=TRUE, dpi=90}


        G1 <- ggplot(data=minidf, aes(x=PROGRAM)) + geom_bar(aes(fill=SCHOOL), alpha=0.8) + coord_flip() +
                theme(legend.position="bottom", legend.key.size=unit(0.5, "cm")) #+
                #theme(axis.text.x = element_text(size=rel(0.5)))
                        #theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position="bottom") 
        G1
```

## Shiny app (cont)

Sample output

```{r code3, echo = FALSE, message=FALSE, eval=TRUE}
        G2 <- ggplot(data=minidf, aes(x=PROGRAM, colour=SCHOOL)) + geom_point(aes(y=DURATION), alpha=0.8, size=4) +
                        theme_bw() +
                        theme(axis.text.x = element_text(size=3.5, angle = 45, hjust = 1), legend.position="bottom")
                
        G2

```

